Trail Saving on Backtrack

### 2020-03-02 paper.tex
used maple data more consistent with definitions

\documentclass[runningheads]{llncs}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%\usepackage[noend]{algcompatible}
%\usepackage[ruled,linesnumbered,noend,oldcommands]{algorithm2e}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[table]{xcolor}
\usepackage{theorem}

@@

In Figure~\ref{fig:cadicalNew} we used the newest version of cadical
(downloaded as of January 1, 2020) as the baseline solver, in
Figure~\ref{fig:cadicalOld} we used the version of cadical published
in \cite{DBLP:conf/sat/MohleB19} as the baseline, and in
Figure~\ref{fig:maple} we used MapleLCMDist \cite{xiao2017maplelrb} as
the baseline. Each of the baselines were run with standard
non-chronological backtracking. We then refer to versions of each
solver with additional features implemented on top by adding
suffixes. "-chrono" refers to the solver with \cbt enabled (using the
solver's default settings), "-trail" refers to the baseline with plain
trail saving added (as described in Figure~\ref{fig:trailUse}),
"-trail-multipleBT" refers to the baseline with trail saving plus the
first enhancement of saving over multiple backtracks,
"-trail-multipleBT-lookahead" also adds the enhancement of lookahead
for conflicts by 2 decision levels, and
"-trail-multipleBT-lookahead-reason" also adds the final enhancement
to cease trail saving once a reason of "low quality" is reached. For
more details on the enhancments, please see section 4.2.

@@

\begin{figure}[t]
\centering
    \begin{tabular}{|l|l|l|l|l|l|}
      \hline
      & Total & SAT & UNSAT & Avg. Par-2 \\ \hline
      cadical                  & 532          & 314 &  218  & 4025                             \\ \hline
      cadical-chrono          & 525          & 308 &  217  & 4086                             \\ \hline
      cadical-trail           & 529          & 310 &  \textbf{219}  & 4060                   \\ \hline
      cadical-trail-multipleBT & 530 & 313 & 217 & 3930 \\ \hline
      cadical-trail-multipleBT-lookahead & 531          & 313 &  218  & 4020                      \\ \hline
      cadical-trail-multipleBT-lookahead-reason & \textbf{538} & \textbf{319} & \textbf{219} & \textbf{3854} \\ \hline
    \end{tabular}
    \caption{Table of results for cadical, version pulled from github as of January 1, 2020.}
    \label{fig:cadicalNew}
\end{figure}

@@

MapleLCMDist (in Figure~\ref{fig:maple}) is another solver that
benefited from \cbt. In this solver trail saving alone solved more
instances than the solver with \cbt did. Adding the first two
enhancements on top of trail saving resulted in solving three more
instances and yielding a better Par-2 score than the solver with
\cbt. Adding the last enhancement of ceasing trail saving on a "low
quality" reason made the performance worse, whether clause size or lbd
was used as the clause quality metric. This suggests that the
enhancements to trail saving have different impacts on different
solvers.

\begin{figure}
\centering
    \begin{tabular}{|l|l|l|l|l|l|}
      \hline
      & Total & SAT & UNSAT & Avg. Par-2 \\ \hline
      maple           & 458          & 259 &  199  & 4746                             \\ \hline
      maple-chrono   & 470          & 271 &  199  & 4613                             \\ \hline
      maple-trail    & 472          & 271 &  \textbf{201}  & 4618                \\ \hline
      maple-trail-multipleBT-lookahead & \textbf{473} & \textbf{278} &  195  & \textbf{4584} \\ \hline
      maple-trail-multipleBT-lookahead-reason & 467 & 273 & 194 & 4668 \\ \hline
    \end{tabular}
    \caption{Table of results for MapleLCMDist.}
    \label{fig:maple}
\end{figure}

>>>>

\documentclass[runningheads]{llncs}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%\usepackage[noend]{algcompatible}
%\usepackage[ruled,linesnumbered,noend,oldcommands]{algorithm2e}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[table]{xcolor}
\usepackage{theorem}
\usepackage{float}

@@

In Figure~\ref{fig:cadicalNew} we used the newest version of cadical
(downloaded as of January 1, 2020) as the baseline solver, in
Figure~\ref{fig:cadicalOld} we used the version of cadical published
in \cite{DBLP:conf/sat/MohleB19} as the baseline, and in
Figure~\ref{fig:maple} we used MapleLCMDist \cite{xiao2017maplelrb} as
the baseline. Each of the baselines were run with standard
non-chronological backtracking. We then refer to versions of each
solver with additional features implemented on top by adding
suffixes. "-chrono" refers to the solver with \cbt enabled (using the
solver's default settings), "-trail" refers to the baseline with plain
trail saving added (as described in Figure~\ref{fig:trailUse}),
"-trail-multipleBT" refers to the baseline with trail saving plus the
first enhancement of saving over multiple backtracks,
"-trail-multipleBT-lookahead" also adds the enhancement of lookahead
for conflicts by 2 decision levels, and
"-trail-multipleBT-lookahead-reason" also adds the final enhancement
to cease trail saving once a reason of "low quality" is reached. For
more details on the enhancements, please see section 4.2.

@@

\begin{figure}[H]
\centering
    \begin{tabular}{|l|l|l|l|l|l|}
      \hline
      & Total & SAT & UNSAT & Avg. Par-2 \\ \hline
      cadical                  & 532          & 314 &  218  & 4025                             \\ \hline
      cadical-chrono          & 525          & 308 &  217  & 4086                             \\ \hline
      cadical-trail           & 529          & 310 &  \textbf{219}  & 4060                   \\ \hline
      cadical-trail-multipleBT & 530 & 313 & 217 & 3930 \\ \hline
      cadical-trail-multipleBT-lookahead & 531          & 313 &  218  & 4020                      \\ \hline
      cadical-trail-multipleBT-lookahead-reason & \textbf{538} & \textbf{319} & \textbf{219} & \textbf{3854} \\ \hline
    \end{tabular}
    \caption{Table of results for cadical, version pulled from github as of January 1, 2020.}
    \label{fig:cadicalNew}
\end{figure}

@@

MapleLCMDist (in Figure~\ref{fig:maple}) is another solver that
benefited from \cbt. In this solver trail saving alone solved two more
instances than the solver with \cbt did. Adding the first two
enhancements on top of trail saving resulted in solving only one more
instance but yielded a better Par-2 score than the solver with
\cbt. Adding the last enhancement of ceasing trail saving on a "low
quality" reason made the performance worse, whether clause size or lbd
was used as the clause quality metric. This suggests that the
enhancements to trail saving have different impacts on different
solvers.

\begin{figure}
\centering
    \begin{tabular}{|l|l|l|l|l|l|}
      \hline
      & Total & SAT & UNSAT & Avg. Par-2 \\ \hline
      maple           & 458          & 259 &  199  & 4746                             \\ \hline
      maple-chrono   & 470          & 271 &  199  & 4613                             \\ \hline
      maple-trail    & \textbf{472}          & 271 &  \textbf{201}  & 4618                \\ \hline
      maple-trail-multipleBT-lookahead & 471 & 272 &  199  & \textbf{4597}        \\ \hline
      maple-trail-multipleBT-lookahead-reason & 467 & \textbf{273} & 194 & 4668 \\ \hline
    \end{tabular}
    \caption{Table of results for MapleLCMDist.}
    \label{fig:maple}
\end{figure}
